---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# package.rb

<!-- badges: start -->
<!-- badges: end -->

Package.rb is all about making it easy to convert and play around with measurements like length, weight, and temperature in R, so you can breeze through your data tasks without breaking a sweat.

## Installation

You can install the development version of package.rb from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("raechlll/package.rb")
```

## Usage

When working with measurements like length, weight, and temperature, you often need to convert between different units. This is where package.rb comes in handy.

```{r}
library(package.rb)

x <- c(2, 3.5, 15, 230)
# Example: Convert temperature from Celsius to Kelvin
convert_temperature(20, from = "C", to = "K")

# Example: Convert length from centimeters to meters
convert_length(150, from = "cm", to = "m")

# Example: Convert weight from kilograms to grams
convert_weight(70, from = "kg", to = "g")
```

